\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-08-20 paper.tex
WIP async actions

\begin{itemize}
    \item Turns any Python function into a background action with the decorator
        \python|@action|.
    \item Robot actions are non-blocking by default: they are instanciated as
        futures (lightweight threads),
    \item Actions can be cancelled at any time via signals (the
        \python|ActionCancelled| signal is raised).
    \item Lock specific resources with a simple \python|@lock(...)| in front of the
        actions. When starting, actions will wait for resources to be
        available if needed.
    \item Supports compound resources (like \python|WHEELS == LEFTWHEEL + RIGHTWHEEL|)
    \item Create event with robot.every(<condition>).do(<action>)
    \item Poses are managed explicitly and can easily be
        transformed from one reference frame to another one
        (integrates with ROS TF when available).
    \item Extensive logging support to debug and replay
        experiments.
\end{itemize}

@@

As they will be executed in independent
threads, these functions may block or never return (typically useful to
implement lasting background behaviours).

Actions can also call each-other, allowing decomposition of
complex tasks into sub-actions and eventually atomic actions.

>>>>

\begin{itemize}
    \item Turns any Python function into a background action with the decorator
        \python|@action|.
    \item Robot actions are non-blocking by default: they are instanciated as
        futures (lightweight threads),
    \item Actions can be cancelled at any time via signals (the
        \python|ActionCancelled| signal is raised).
    \item Lock specific resources with a simple \python|@lock(...)| in front of the
        actions. When starting, actions will wait for resources to be
        available if needed.
    \item Supports compound resources (like \python|WHEELS == LEFTWHEEL + RIGHTWHEEL|)
    \item Create event with \python|robot.every(<condition>).do(<action>)|
    \item Poses are managed explicitly and can easily be
        transformed from one reference frame to another one
        (integrates with ROS TF when available).
    \item Extensive logging support to debug and replay
        experiments.
\end{itemize}

@@

\emph{Actions} in \pyRobots are always asynchronous. They are implemented as
\emph{futures} (also known as \emph{promises}) and therefore executed in
independent threads. To the developer, however, they appear as regular Python
function, simply annotated with the \python|@action| decorator, and are invoked
as any other function.  Since they are asynchronous, these functions may
perfectly block or even never return (typically useful to implement lasting
background behaviours).

Actions can also call each-other, allowing natural decomposition of complex
tasks into sub-actions and eventually atomic actions.

\paragraph{Signaling} Running behaviours often need to be paused of cancelled.
This poses a particular challenge in robotics, because before suspending an
action, one often want to bring back the robot in some form of rest state (you
would not want to suddenly cancel a \python|walk| action in the middle of a step
without first bringing back the foot to the ground).

\pyRobots addresses this issue by the mean of signals, and extends standard
Python thread into \emph{signaling threads}. Listing~\ref{lst:signals}
illustrates this mechanism.

\begin{listing}[H]
\begin{pythoncode}
    @action
    def my_action(robot):
      try:
        robot.do_something_dangerous()
      except ActionCancelled:
        robot.go_back_to_rest_pose()

    action = robot.my_action()
    time.sleep(1)
    action.cancel()
\end{pythoncode}
\caption{Handling a cancellation signal}
\label{lst:signals}
\end{listing}
